
\section*{Acknowledgements}
  I wish to express my deepest gratitude to Dr. Bertram Bitsch for giving me 
  the opportunity of writing my bachelor's thesis under his supervision at the 
  Max Planck Institute for Astronomy. I am very grateful to him for always 
  being available with helpful answers to the questions and problems facing me 
  during the writing of this work. \\
  \\
  I want to thank Camille Bergez-Casalou as well, who quite a few times helped 
  me out with friendly advice when it came to the intricacies of the FARGO2D1D 
  code or the usage of the computer cluster. \\
  % and for partly being responsible for me learning French again
  \\
  Also, I am very grateful to Prof. Dr. Kees Dullemond for taking on the task 
  of acting as second examiner, as well as Dr. Coryn Bailer-Jones, for 
  inspiring me during a seminar to write my bachelor's thesis at the MPIA and 
  for helping me establish contact with Bertram. In general, I wish to express 
  my gratitude to Ruperto Carola University and to the MPIA Heidelberg, for the 
  knowledge and opportunities they granted me. \\
  \\
% I had a great time at the MPIA 
%    - always there when advice was needed 
%    - helping, nice
%
%  Camille Bergez-Casalou
%    - answered questions about the numerical algorithm 
%
%  Prof. Kees Dullemond
%    - 2nd correcteur
%
%  MPIA
%    - organization
%    - staff: great working climate, fun to go there
%    - always new things to learn in group meetings, kept me curious
%    - including:
%
%  Coryn Bailer-Jones 
%    - in his seminar, he inspired me to do my thesis at the MPIA
%    - helped me in establishing contact with Bertram
%
%  Physics Department of the Ruperto Carola university
%    - for giving me the opportunity to study physics in Heidelberg
%
  % papa
  Lastly, I wish to thank my mother for making it possible for me to study 
  physics in Heidelberg, as well as my father and grandmother, who from an 
  early age on inspired me 
  % to think critically and to remain 
  to be curious about the universe.
%  Mother 
%    - without whose financial support during my time at university this 
%      work definitely would not have been possible
%
%  Grandmother
%    - from an early age inspired me to think critically and be curious about 
%      the universe
%
%  Selina ?
%    - kept me going, emotional support (?)
%
